Of judges, aliens and total preorders

### 2021-02-02 paper/1901_3230880_philip_heltweg.tex
feat: explained belief set expansion, contraction and revision

%Consider a knowledge base (KB) represented by a set of sentences in a
%language L. As our perception of the world described by the knowledge base
%changes, the knowledge base must be modified. G~irdenfors [9] distinguishes
%several kinds of modifications. If we simply acquire additional knowledge
%about the world, and the new knowledge does not conflict with the current
%beliefs t of the KB, we expand the KB. If, however, the new knowledge is
%inconsistent with the old beliefs, and we want the KB to be always consistent,
%we must resolve the conflict somehow; this operation will be called revision. A
%* Part of this work was performed while this author was visiting the University of Toronto.
%** This author is partially supported by the Natural Science and Engineering Research Council
%of Canada.
%1 We use the terms belief and knowledge interchangeably in this paper.
%0004-3702/91/$03.50 © 1991 -- Elsevier Science Publishers B.V. All rights reserved 
%264 H. Katsuno, A.O. Mendelzon
%different kind of change occurs when a sentence previously believed becomes
%questionable and has to be given up; the operation that makes this change is a
%contraction

@@

\subsection{Belief sets and epistemic states}
\label{chapter:belief-sets-and-epistemic-states}
% TODO: explain contraction, revision, expansion
% ANSWER: Ich würdes es ganz kurz erläutern im Text. Im Vortrag vielleicht nicht umbedingt.

% TODO: Gardenfors correct? read!
A belief set is the deductively closed set of propositions an agent accepts as true at any given point in time \cite{Ferme2011}. Alchourrón, Gärdenfors, and Makinson (AGM theory, \cite{Alchourron1985}) define postulates for belief sets and their contraction, expansion or revision with new evidence. In the process of belief revision an agent keeps their set of beliefs consistent while incorporating new information, even if it is inconsistent with the current belief set \cite{Gaerdenfors1984}. Darwiche and Pearl \cite{Darwiche1997} argue that working with belief sets is not expressive enough for satisfying results in iterated belief revision. They make the distinction between propositional beliefs (beliefs the agent accepts and are part of the belief set) and conditional beliefs as beliefs the agent is prepared to adopt with new evidence.

>>>>

@@

\subsection{Belief sets and epistemic states}
\label{chapter:belief-sets-and-epistemic-states}
% TODO: explain contraction, revision, expansion
% ANSWER: Ich würdes es ganz kurz erläutern im Text. Im Vortrag vielleicht nicht umbedingt.
% TODO: Gardenfors correct? read!
A belief set is the deductively closed set of propositions an agent accepts as true at any given point in time \cite{Ferme2011}. Alchourrón, Gärdenfors, and Makinson (AGM theory, \cite{Alchourron1985}) define postulates for belief sets and their expansion, contraction or revision with new evidence. Belief set expansion is the process of incorporating a new piece of evidence that is not inconsistent with currently held beliefs while contraction refers to giving up a belief that has become questionable. The process of belief revision refers to keeping an agent's set of beliefs consistent while incorporating new information that is inconsistent with the current belief set \cite{Katsuno1991, Gaerdenfors1984}. Darwiche and Pearl \cite{Darwiche1997} argue that working with belief sets is not expressive enough for satisfying results in iterated belief revision. They make the distinction between propositional beliefs (beliefs the agent accepts and are part of the belief set) and conditional beliefs as beliefs the agent is prepared to adopt with new evidence.
